Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-29 WSSSPE3/report/WSSSPE3_review.tex
Add travel awardees.
Fixed some punctuation in Intro

This report is based on collaborative notes taken with during the workshop,
which were linked from the GitHub issues that represented the potential and
actual working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}); the keynotes (\S\ref{sec:keynote}); a series of
lightning talks (\S\ref{sec:lightning}), intended to give an opportunity for
attendees to quickly highlight an important issue or a potential solution. The
report also gives summaries of action plans proposed by the eleven working
groups (\S\ref{sec:WGs}), and some conclusions (\S\ref{sec:conclusions}).
Finally, the report includes a list of registered attendees
(Appendix~\ref{sec:attendees}) and longer descriptions of the activities that
occurred in each of the working groups that made substantial progress.
(Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}.)

@@

Turk talked about possible reasons why we want to sustain scientific
software: devotion to science and interests in pursuing the next stage of
research; fun and creative thrill in writing codes and papers; usefulness with
measurable impacts, for example, LINPACK and HDF groups providing of data
storage to satellites, which goes beyond usefulness to necessity. Lastly, Turk
presented his wishlist of questions to be answered: 
%
\begin{itemize}

@@

>>>>

This report is based on collaborative notes taken with during the workshop,
which were linked from the GitHub issues that represented the potential and
actual working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}); the keynotes (\S\ref{sec:keynote}); a series of
lightning talks (\S\ref{sec:lightning}), intended to give an opportunity for
attendees to quickly highlight an important issue or a potential solution. The
report also gives summaries of action plans proposed by the eleven working
groups (\S\ref{sec:WGs}), and some conclusions (\S\ref{sec:conclusions}).
Finally, the report includes a list of registered attendees
(Appendix~\ref{sec:attendees}) and longer descriptions of the activities that
occurred in each of the working groups that made substantial progress 
(Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}).

@@

Turk talked about possible reasons why we want to sustain scientific
software: devotion to science and interests in pursuing the next stage of
research; fun and creative thrill in writing codes and papers; usefulness with
measurable impacts, for example, LINPACK and HDF groups providing of data
storage to satellites, which goes beyond usefulness to necessity. Lastly, Turk
presented his wishlist of questions to be answered in the future: 
%
\begin{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Travel Award Recipients}  \label{sec:awardees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}
The following is list of travel award recipients for the WSSSPE3 workshop.

{\scriptsize
\begin{longtable}{lll}
\input{awardees}
\end{longtable}
}
